\Large Co-evolution of lexical meaning \& pragmatic use\\ {\bf Revision Cover letter}

### 2018-03-30 paper/rv-letter1.tex
final manuscript+letter changes TB

\vspace{.5cm}
\begin{mdframed}[backgroundcolor=gray!25,linecolor=gray!25]
Also [in the Subsection {\em learnability only}], why isn't the proportion of Lall highest, given that it has the lowest complexity (highest prior)?
\end{mdframed}
%
\mf{We need to possibly rewrite this.}
Due to their stochastic speaker behavior, the data produced by $L_{\text{all}}$-teachers tends to be compatible with the behavior of many other types. Intuitively, the data such teachers produce are all over the place and do not do a good job in setting them apart from other types. Consequently, even if the prior favors $L_{\text{all}}$, this type is not transmitted very faithfully; learners reason that the input they get from $L_{\text{all}}$-teachers could also come from other types and may adopt those instead. If there are types that are transmitted more faithfully, the population will, over time, transition to these types rather than to $L_{\text{all}}$. As we put it in Section~4, iterated learning does not necessarily promote the {\em a priori} more likely type, but tends to promote a type $t$ based on a gradient of how many other types might likely mutate into $t$, so to speak. We stress this in Section~3.2.2 and Section~4.

>>>>

\vspace{.5cm}
\begin{mdframed}[backgroundcolor=gray!25,linecolor=gray!25]
Also [in the Subsection {\em learnability only}], why isn't the proportion of Lall highest, given that it has the lowest complexity (highest prior)?
\end{mdframed}
%
As now made much more explicit in the discussion surrounding iterated learning and the {\em learnability only} condition, a population that approximates the prior (with, e.g., $L_{\text{all}}$ as the highest) is only guaranteed for $l = 1$ (in line with the analytic results from \citealt{griffiths+kalish:2007}). For $l > 1$ matters are different. The reason why we do not see $L_{\text{all}}$ come out as the majority type are asymmetries in types' production behavior (see appendix C and \S3.3.1). Due to their stochastic speaker behavior, the data produced by $L_{\text{all}}$-teachers tends to be compatible with the behavior of many other types. Intuitively, the data such teachers produce are all over the place and do not do a good job in setting them apart from other types. In fact, the data may be ``misleading'' and suggest a different type. Consequently, even if the prior favors $L_{\text{all}}$, this type is not transmitted very faithfully; learners reason that the input they get from $L_{\text{all}}$-teachers could also come from other types and may adopt those instead. If there are types that are transmitted more faithfully under the same parameter constellation, the populationmay, over time, transition to these types rather than to $L_{\text{all}}$. As we put it in Section~4, iterated learning does not necessarily promote the {\em a priori} more likely type, but tends to promote a type $t$ based on a gradient of how many other types might likely mutate into $t$, so to speak. We now stress this more in Section~3.2.2, Section~4, and appendix C.
